---
title: "fortunecookie"
author: " "
date: " "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<br>


#### Plumber API with an endpointnamed "subsetdata"

The subsetdata API takes user's values of a particular variables of the dataset (using post method to receive data) and return data filtered to a subset of rows in the dataset
The iris dataset is used as an example. 



##### Setup

```{r, message=F}
library(datasets)
library(dplyr)
```


<br>

##### Step 1: Write down the functions and save it to a file called "plumber2.R" in the same directory

```{r,eval=F, echo=T}
# plumber2.R

#* Subset the data according to certain parameter
#* @param variable The variable used  
#* @param accept.value The value of the column used to filter the data.
#* @post /subsetdata
function(variable, accept.value){
  
    if(is.numeric(iris[variable]))    
           iris %>% 
             subset(., iris[variable] > as.numeric(accept.value))
  else 
           iris %>% 
             subset(., iris[variable] == accept.value)
}

```


<br>
 
##### Step 2: Run this part (the link http://127.0.0.1:8001/__swagger__/ should open)


```{r,eval=F, echo=T}

p2 <- plumb("plumber2.R")  # Where 'plumber.R' is the location of the file shown above
p2$run(port=8001)

```


<br>

##### Step 3: In a diffrent session (Session -> New Session) test the function


```{r,eval=F, echo=T}

# USE POST QUERY ARGUMENTS

test2 <- POST("http://localhost:8001/subsetdata", query = list(variable = 'Species', accept.value = 'setosa'))

content(test2)
```

<br>



